Fitting metabolic models to dissolved oxygen data: the Estuarine BAyesian Single-station Estimation method

### 2023-05-04 manu-draft.qmd
additional scratch text to discussion

The second improvement of EBASE over alternative methods was the several modifications to

@@

>>>>

The second improvement of EBASE over alternative methods was the several modifications to .... Primary modifications (Production is linearly related to PAR (aPAR), not saturation point Respiration is constant (not temp dependent), Uses a gas exchange commonly used in oceanic systems (not littoral - streams/lakes as in Grace)).  this also reduces the data requirements by not needing...

@@

Some limitations of EBASE include still relatively long time to fit the model compared to other methods, e.g., Odum, but this is not unique to EBASE and other MCMC Bayesian approaches have similar constraints.  Some options can be changed to decrease time for model fitting, or multiple cores can be used.  Another limitation is the need for the user to choose priors and optimization periods, although we provide some suggestions above.  Our extensive analysis evaluating effects on priors and optimization period provide some guidance. As a comparison, the detiding method requires a user to choose windows and the guidance is xyz, although the sensitivity analysis was not informed by known results.  Our use of the EBASE model formula to generate a synthetic time series with known parameters is a significant improvement over the former analysis and our suggestions can be take with more confidence.  Although this is limited to Apalachicola data, the broad suggestion to user unconstrained priors will likely expand to other system with different characteristics.
